### 2016-07-27 syntax.tex
updating syntax of data structures, and adding set-multiplicity data structures
cheers

\heading{Bloom Filters and Related Data Structures. }
It is not hard to see Bloom filters are one possible instantiation a set-multiplicity data structure.
Fix an $n \geq 0$, let $\mathcal{S}=[\univ]^n$, and let $\Sigma=\Gamma=\bits$.  
Define the queries so that $q_x(S)=1$ if $x \in S$, and 0 otherwise.  Define algorithm~$\Rep$, with functions $k=k(|S|), m=m(|S|)$ and a description of a hash function family~$\mathcal{H}=\{h \colon \univ \to \{1,2,\ldots,m\}\}$ hardwired into it, to sample hash functions $h_1, \ldots, h_k$ from~$\mathcal{H}$ and then compute an $m$-bit array in the standard way.  It sets $\aux = (h_1, \ldots, h_k)$ and $M$ to be the bit array, and returns these.  The algorithm~$\Qry$ is defined so that, on input $(M,\aux,q_x)$, it returns the minimum of the values (either 0 or 1) held at $M[h_1(x)],\ldots,M[h_k(x)]$.  We note that, while our error-probability and error-rate do not distinguish among ``types'' of errors, they also do not preclude instantiations (like the classical Bloom filter) that admit only one type of error, e.g. false-positives.

As a simple extension, consider $\Sigma=\mathbb{N}$ and a scheme that stores counters at each position in an array.  In particular, for each~$x \in S$ the $\Rep$~algorithm increments the counters stored at positions $h_1(x), h_2(x), \ldots, h_k(x)$, returns the final array of counters as~$M$.  The $\Qry$-algorithm remains the same. Such a construction gives a static version of a counting Bloom filter~\cite{xxx}.  We will capture dynamic versions, as well as count-min sketches, scalable Bloom filters, etc., in a later section.

>>>>

%\heading{Bloom Filters and Related Data Structures. }
It is not hard to see Bloom filters are one possible instantiation a set-multiplicity data structure.
Fix an $n \geq 0$, let $\mathcal{S}=[\univ]^n$, and let $\Sigma=\Gamma=\bits$.  
Define the queries so that $q_x(S)=1$ if $x \in S$, and 0 otherwise.  Define algorithm~$\Rep$, with functions $k=k(|S|), m=m(|S|)$ and a description of a hash function family~$\mathcal{H}=\{h \colon \univ \to \{1,2,\ldots,m\}\}$ hardwired into it, to sample hash functions $h_1, \ldots, h_k$ from~$\mathcal{H}$ and then compute an $m$-bit array in the standard way.  It sets $\aux = (h_1, \ldots, h_k)$ and $M$ to be the bit array, and returns these.  The algorithm~$\Qry$ is defined so that, on input $(M,\aux,q_x)$, it returns the minimum of the values (either 0 or 1) held at $M[h_1(x)],\ldots,M[h_k(x)]$.  We note that, while our error-probability and error-rate do not distinguish among ``types'' of errors, they also do not preclude instantiations (like the classical Bloom filter) that admit only one type of error, e.g. false-positives.

As a simple extension, consider $\Sigma=\mathbb{N}$ and a scheme that stores counters at each position in an array.  In particular, for each~$x \in S$ the $\Rep$~algorithm increments the counters stored at positions $h_1(x), h_2(x), \ldots, h_k(x)$, returns the final array of counters as~$M$.  The $\Qry$-algorithm remains the same. Such a construction gives a static version of a counting Bloom filter~\cite{xxx}.  We will capture dynamic versions, as well as count-min sketches~\cite{xxx}, scalable Bloom filters~\cite{xxx}, etc., in a later section.
